---
title       : ShinyApp - IRIS Dataset
subtitle    : Course Project - Shiny Application and Reproducible Pitch
author      : LKNGIN
job         : 2016
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
--- .class #id 
## Overview

This application was built as per the requirements stated in the course assignment **Developing Data Products - Your Reproducible Pitch Presentation**

The first part of the assignment, **Your Shiny Application**, is avalilable at:
https://buzzmapper.shinyapps.io/Shinyapps/

Source code for ui.R and server.R files are available on the GitHub repo:
https://github.com/lkngin/Coursera.git

--- .class #id 
## Web Application functionality
The Web Application is reactive and is a useful tool to explore the Iris dataset.

User can select one of the 4 variables, Sepal.Length, Sepal.Width, Petal.Length, Petal.Width, to be shown in the graph interactively.

The user can also select the colour to be plotted for the Histogram.

--- .class #id 
## IRIS Dataset

The data used in the app comes from the (iris) dataset. 
iris dataset summary:
```{r, echo=FALSE}
summary(iris)
```

--- .class #id 
## Plot
```{r, echo=FALSE}
iris$Colour <- ""
iris$Colour[iris$Species=="setosa"] <- "magenta"
iris$Colour[iris$Species=="versicolor"] <- "cyan"
iris$Colour[iris$Species=="virginica"] <- "yellow"

plot(iris$Sepal.Length, iris$Petal.Length, col = iris$Colour, pch = 16, cex = 2)
legend(x = 4.5, y = 7, 
       legend = c("setosa","versicolor","virginica"),
       col = c("magenta","cyan","yellow"),
       pch=16)
```

